\subsection{Basics}
A homography is a projective transformation from one space to another. It can
be applied to a point to project that point onto another space. Consequently,
it can be applied to an entire space, to project it onto another. 

Here we discuss only transformations in two-dimensional spaces, i.e. planes.
We denote the homography from a plane $I$ to a plane $J$ as $H_{I}^{J}$ and
inversely, the homography from $J$ to $I$ is written as $H_{J}^{I}$.

The operations performed by a homography can be described as any combination of
\begin{itemize}
	\item Translation
	\item Rotation
	\item Scaling
	\item Reflecting
	\item shearing/skewing
\end{itemize}

Translation is the simple operation of moving a point to another, by adding
scalars to the points coordinates. Essentially a point
$\big(\begin{smallmatrix}
	x \\
	y
\end{smallmatrix}\big)$
can be translated by 
$\big(\begin{smallmatrix}
	\Delta x \\
	\Delta y
\end{smallmatrix}\big)$
, making the new point
$$\begin{pmatrix}
	x' \\
	y'
\end{pmatrix}
=
\begin{pmatrix}
	\Delta x+x \\
	\Delta y+y
\end{pmatrix}$$

Rotation is the rotation of a point $(x,y)$ by an angle $\theta$, or rather the
rotation of a vector from the origin to a point, by an angle.
$$\begin{bmatrix}
	x' \\
	y'
\end{bmatrix}
=
\begin{bmatrix}
	\cos \theta & -\sin \theta \\
	\sin \theta & \cos \theta
\end{bmatrix}
*
\begin{bmatrix}
	x \\
	y
\end{bmatrix}$$
The matrix
$\big[\begin{smallmatrix}
	\cos \theta & -\sin \theta \\
	\sin \theta & \cos \theta
\end{smallmatrix}\big]$
is called the \emph{rotation matrix}.

Scaling refers to the multiplication of scalars and a point.
$$\begin{bmatrix}
	x' \\
	y'
\end{bmatrix}
=
\begin{bmatrix}
	S_{x} & 1 \\
	1 & S_{y}
\end{bmatrix}
*
\begin{bmatrix}
	x \\
	y
\end{bmatrix}$$
When $S_{x} = S_{y}$ the aspect ratio will remain the same as before the
transformation.

Reflecting is the special case when either or both scaling parameter are
negative, hence reflecting points around the coordinate systems axes.

Shearing or skewing is a transformation that wont respect angles, and is
obtained by
$$\begin{bmatrix}
	x' \\
	y'
\end{bmatrix}
=
\begin{bmatrix}
	1 & Sh_{x} \\
	Sh_{y} & 1
\end{bmatrix}
*
\begin{bmatrix}
	x \\
	y
\end{bmatrix}$$
